Verifying Demonstrations

### 2018-08-20 paper/intro.tex
Updates system, adversary model section

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{system-model}).  
Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
terms of these properties (\cref{related-work}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{building-blocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
Finally, we conclude with a discussion \cref{Discussion} and future work in \cref{Conclusion}.

>>>>

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
}
\emph{Outline.} 
The paper is organized as follows. 
First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{system-model}).  
Then, we introduce the desired security properties for such a system (\cref{security-properties}) and subsequently discuss related work in 
terms of these properties (\cref{related-work}). 
Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{building-blocks}). 
\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
Finally, we conclude with a discussion \cref{Discussion} and future work in \cref{Conclusion}.

### 2018-08-20 paper/system-model.tex
Updates system, adversary model section

\section{System model}

\include*{protest-model}
\include*{security-properties}

>>>>

\section{System and adversary model}%
\label{system-model}

We will now describe our system and adversary models.
We first present an abstraction of a protest and how to count the participation 
(\cref{protest-model}).
Next we present the communication and adversary model (\cref{adversary-model}).
Finally, we present the desired security properties 
(\cref{security-properties}).

\include*{protest-model}
\include*{adversary-model}
\include*{security-properties}
